### 2021-07-14 doc/thesis/chapters/implementation.tex
analysis

\section{GNU Radio}
  \subsection{Introduction}
  \subsection{Transmitter}
  \subsection{Receiver}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Receiver}

The receiver is implemented, following the block diagram in Fig.\ref{fig:bd_dsp_detailed}.
Further assumptions and simplifications, such as the fixed point arithmetic are described into detail above.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Analysis}

The Matlab implementation also includes a comprehensive range of analysis, especially in terms of visual plots.
These plots are useful during the development of new DSP algorithms, in order to verify the correct thereof.\\

An example of a plot that is created by the analysis is depicted in Fig.\ref{fig:matlab_analysis_time_domain}.
The diagram shows the respective signals in the time domain.
Above two timelines display the input data, as it is read from the input audio file.
The two diagrams in the center plot the Mono and LR Diff signals.
The bottom diagrams then represent the result after the entire signal processing chain.
It can be seen that the DSP chain is not able to demodulate the original signal without any error.
However, the result shows a clear separation of the left and right channels, as resembles the original input very closely, which is good enough for this case study.\\

\includepicture [1.0] [0] {Matlab analysis in the time domain.} {matlab_analysis_time_domain} {img/matlab/matlab_analysis_time_domain}

Further analysis is done in the frequency domain, especially in order to better understand the modulation of the different spectral parts in the FM channel.
An example thereof is shown in Fig.\ref{fig:matlab_analysis_freq_domain}.

The spectrum of an FM channel, as it is generated by a transmitter before the modulation, is shown in the upper diagram.
The spectrum after the demodulation through a receiver is shown in the lower diagram.
Spectral parts, such as the pilot tone at 19 kHz, or the LR Diff part around 38 kHz can be seen clearly.
The demodulated spectrum shows an artifact at 57 kHz, which does not exist in the original transmitter spectrum.
This is an artifact of the demodulation process, specifically the frequency-shift of the LR Diff part to baseband.
The artifact is very low in energy, because it is attenuated by a BP filter in the down-conversion process, and can thus be ignored for further processing, even though it can still be seen in the spectral analysis.

\includepicture [1.0] [0] {Matlab analysis in the frequency domain.} {matlab_analysis_freq_domain} {img/matlab/matlab_analysis_freq_domain}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{GNU Radio}
  \subsection{Introduction}
  \subsection{Transmitter}
  \subsection{Receiver}
